\LARGE \bf WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators

### 2014-09-30 paper2015asml.tex
finished writing unary features, tweaked some text, changed some figures, added new screenshots

\begin{figure*}
\centering
\begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[trim = 0mm 0mm 0mm 0mm, width=\textwidth]{pictures/drawer_scene}
    \caption{}
    \label{drawer_scene}
  \end{subfigure}%
  ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
%(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.25\textwidth}
    \includegraphics[trim = 0mm 0mm 0mm 0mm, width=\textwidth]{pictures/countertop_scene}
    \caption{}
    \label{fig:countertop_scene}
  \end{subfigure}
  ~ %add desired spacing between images, e. g. ~, \quad, \qquad etc.
%(or a blank line to force the subfigure onto a new line)
  \begin{subfigure}[b]{0.38\textwidth}
    \includegraphics[trim = 0mm 0mm 0mm 0mm, width=\textwidth]{pictures/industrial_scene}
    \caption{}
    \label{fig:industrial_scene}
  \end{subfigure}
\caption{The scenes used in generating the library of robot motions to collect feedeback for. (a) \emph{Drawer} (b) \emph{Countertop} and (c) \emph{Industrial}}\label{fig:scenes}
\end{figure*}

@@

\begin{figure}[b]
    \includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/designing_queries_moveit}
    \caption{Screenshot of the planning query design process which involved hand-picking start and goal query poses for the various scenes manually to ensure they were neither trivial nor impossible for the planning algorithms to solve. This was accomplished through use of RVIZ and interactive markers.}
    \label{fig:design}
\end{figure}

@@

\begin{figure}
    \frame{\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_survey_screenshot}}
    \caption{The main survey question which prompts the participant for a rating in four motion characteristics (efficiency, elegance, smoothness and overall impression) after presenting a video that demonstrates the motion from four clearly visible vantage points for any sample trajectory.}
    \label{fig:survey_question}
\end{figure}

@@

\begin{figure}
\frame{\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_control_question}}
\caption{The survey control question which prompts the participant about the action of the robot in the accompanying video. The question we adopted was to ask the particpant which colored cube the robot touched.}
\label{fig:control_question}
\end{figure}

@@

@@

@@

@@

@@

\subsubsection{Curvature}

@@

We compared the trajectories to nominal end-effector trajectories that were created using a breadth first search in a 3D voxel approximation of the planning problem. The planning scene is discretized, and voxels are marked as occupied or empty if any part of the voxel is considered in collision with the underlying planning scene. The start and goal voxel is simply the $(x,y,z)$ of the end-effector tool-frame. Note that this does not take into account the orientation of the end-effector. These voxels make up our vertices $V_\text{grid}$ for our graph.

The edges $E_\text{grid}$ used in this search are the 26-connected grid of adjacent neighboring voxels that are one unit step away in any direction. For example, some valid adjacent voxels can be computed by adding $(+\Delta x,0,0)$, $(-\Delta x,-\Delta y,0)$, and $(+\Delta x, -\Delta y,-\Delta z)$ to the coordinates of the current voxel. For this graph, $\Delta x = \Delta y = \Delta z = 1$. An edge only exists in this graph if the ending voxel is collision.

The order the neighboring voxels are generated is decided by the length of the line connecting the voxel centers. This results in the voxel-neighbors that share \emph{faces} being pushed onto the queue before the voxel-neighbors that share an \emph{edges}, which are in turn added before those voxel-neighbors that share a \emph{corner} with the generating state. For example, the voxel at $(1,0,0)$ is added to the queue before $(1,1,0)$ which is added before $(1,1,1)$, provided all three are collision free.

We make special mention of this because it can lead to differently shaped (but the same overall length) paths if you were to generate the edges with any other order. This lets us use a simple BFS to search the graph with unit cost edges.

Defining our searchable graph to be $G=(V_\text{grid}, E_\text{grid})$, we can now perform breadth first search on the graph to get a valid collision free path from $V_\text{start}$ to $V_\text{end}$. The resulting path is given a nominal timing and we refer to it as $\xi_{\text{BFS}}$. We compute comparison features between it and three other workspace trajectories that are computed from the forward kinematics of the joint-space trajectory for the following links in the kinematic chain of the manipulator: for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$).

@@

\todo Write about:
\begin{itemize}
\item clearance
\item smoothness
\item angular distance
\item path length
\item figures for examples of high-low values of the above
\end{itemize}

>>>>

\begin{figure}
\centering
  \includegraphics[trim = 70mm 0mm 70mm 0mm, width=0.62\columnwidth, clip=true]{pictures/countertop_scene2}
  \begin{minipage}[b][][s]{0.352\columnwidth}
  \centering
    \includegraphics[trim = 70mm 0mm 70mm 0mm, width=\textwidth, clip=true]{pictures/drawer_scene2}
    \vfill
    \includegraphics[trim = 30mm 0mm 30mm 0mm, width=\textwidth, clip=true]{pictures/industrial_scene2}
  \end{minipage}
\caption{The scenes used in generating the library of robot motions to collect feedeback for. \emph{Drawer} (top right), \emph{Countertop} (left), and \emph{Industrial} (bottom right)}\label{fig:scenes}
\end{figure}

@@

%\begin{figure}[b]
%    \includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/designing_queries_moveit}
%    \caption{Screenshot of the planning query design process which involved hand-picking start and goal query poses for the various scenes manually to ensure they were neither trivial nor impossible for the planning algorithms to solve. This was accomplished through use of RVIZ and interactive markers.}
%    \label{fig:design}
%\end{figure}

@@

%\begin{figure}
%    \frame{\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_survey_screenshot}}
%    \caption{The main survey question which prompts the participant for a rating in four motion characteristics (efficiency, elegance, smoothness and overall impression) after presenting a video that demonstrates the motion from four clearly visible vantage points for any sample trajectory.}
%    \label{fig:survey_question}
%\end{figure}

@@

%\begin{figure}
%\frame{\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_control_question}}
%\caption{The survey control question which prompts the participant about the action of the robot in the accompanying video. The question we adopted was to ask the particpant which colored cube the robot touched.}
%\label{fig:control_question}
%\end{figure}

@@

Here we detail the features we computed on the trajectory \tj{} with waypoints $q_i$ where $i={0,\mathellipsis,n}$ and $n=|\tj{}|$.

@@

The length of the trajectory \tj{} computed as the sum over trajectory segments of the euclidean distance between end points of the segment, or

\begin{equation}
\text{Length} = \sum_{i=0}^{n-1} \| q_\text{i}-q_\text{i+1} \|
\end{equation}

We compute Path Length for the joint space trajectory and for three workspace trajectories that are dervied from the forward kinematic map of the joint-space trajectory for the following links in the kinematic chain: for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$).

@@

The average clearance of a trajectory \tj{} is the average minimum distance of configurations at waypoints to the closest obstacle, or

\begin{equation}
\text{Clearance} = \frac{1}{n} \sum_{i=0}^n \min_{o \in O} \text{dist}(q_i, o)
\end{equation}

where $O$ represents the set of obstacles in the scene and $\text{dist}(q_i, o)$ calculates the closest distance between the kinematic bodies of obstacle $o$ and configuration $q_i$.

@@

The smoothness of a trajectory is computed by averaging the included angle of three consecutive waypoint configurations, for all triplets of waypoints in \tj{}. The angle is computed using joint-space euclidean distance between configurations as the length of sides of the triangle.

\begin{equation}
\begin{aligned}
&\text{Smoothness} = \frac{1}{n-2} \sum_{i=1}^{n-1} \mathellipsis\\
&\left[ \pi- \text{angle}(\|q_\text{i-1}-q_\text{i}\|,\|q_\text{i}-q_\text{i+1}\|,\|q_\text{i+1}-q_\text{i-1}\|) \right]\\
\end{aligned}
\end{equation}

where the included angle is computed

\begin{equation}
\text{angle}(a,b,c) = \arccos (a^2+c^2-b^2)/2ac
\end{equation}

We compute smoothness for the joint-space trajectory \tj{} and for workspace trajectories $\xi_\text{elbow}$, $\xi_\text{wrist}$, and $\xi_\text{tip}$.

@@

For a joint-space trajectory \tj{} consisting of waypoints, the maximum acceleration is computed by finding the accelerations at the knot points of splines fit to each joint's trajectory. The maximum over waypoints of the norm of these accelerations is the feature

\begin{equation}
\text{Max Acceleration} = \max_{i={0,\mathellipsis,n}} {\ddot{q}_i}^T\ddot{q}_i
\end{equation}

We compute maximum acceleration for the joint-space trajectory \tj{} and for workspace trajectories $\xi_\text{elbow}$, $\xi_\text{wrist}$, and $\xi_\text{tip}$.

\subsubsection{Maximum Radius of Curvature}

Curvature at a given waypoint is computed by first fitting the work-space trajectory with splines for each coordinate and computing from the higher order derivatives

\begin{equation}
R_i = \frac{\|\dot{q}_i\|^3}{\|\dot{q}_i \times \ddot{q}_i\|}
\end{equation}

where velocity $\dot{q}_i$ and acceleration $\ddot{q}_i$ are computed at the waypoint $i$ from differentiating the interpolating spline of the work-space trajectory. Alternatively, the higher order derviatives can be computed using finite differencing methods.

We compute maximum curvature for only the workspace trajectories $\xi_\text{elbow}$, $\xi_\text{wrist}$, and $\xi_\text{tip}$.

@@

We compared the trajectories to nominal end-effector trajectories that were created using a breadth-first search in a 3D voxel approximation of the planning problem.

The planning scene is discretized, and voxels are marked as occupied or empty if any part of the voxel is considered in collision with the underlying planning scene.

The start and goal voxel is simply the $(x,y,z)$ of the end-effector tool-frame. The free voxels then make up our vertices $V_\text{grid}$ for our graph.

The edges $E_\text{grid}$ used in this search are the 26-connected grid of adjacent neighboring voxels. For example, some valid adjacent voxels can be computed by adding $(\Delta x,\Delta y,\Delta z)$ to the current coordinates, where $\Delta x= \Delta y= \Delta z= {\pm1,0}$. An edge only exists in this graph if the ending voxel is collision.

The order the neighboring voxels are generated by the breadth-first search is done such that neighboring voxels that share \emph{faces} are pushed onto the queue before those that share an \emph{edge}, which are then added before those that share a \emph{corner} with the generating state. This lets us use a simple BFS to search the graph with unit cost edges.

Using the graph $G=(V_\text{grid}, E_\text{grid})$, we perform breadth-first search to get a collision free path from $V_\text{start}$ to $V_\text{end}$. The resulting path is given a nominal timing and we refer to it as $\xi_{\text{BFS}}$.

We compute comparison features between $\xi_{\text{BFS}}$ and three other workspace trajectories that are computed from the forward kinematic map of the joint-space trajectory for various links in the kinematic chain, which are the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$).

@@

\todo Write about:
\begin{itemize}
\item clearance
\item smoothness
\item angular distance
\item path length
\item create question table
\item get example trajectories (without elbow path)
\item get example snapshots high-low values of features
\end{itemize}
